Robust positively invariant sets for state dependent and scaled disturbances

### 2015-03-19 draft.tex
edited sections II and II - please check proof of Lemma 3.1 carefully!

\section{Introduction}
The analytic properties of disturbance invariant sets have been widely studied (see e.g.~\cite{blanchini:2007}) since their introduction in~\cite{Glover:1971}. A disturbance invariant set $\mathscr X$ is a subset of the state constraint set $\mathcal X_0\subseteq\mathbb R^n$ that contains states $x$ of the perturbed linear system
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v
\end{equation}
(where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$, and 
$v\in\mathscr V$) such that the successor state $x^+$ is contained in the 
disturbance invariant set for all possible realisations of the 
unknown disturbance $v$. This is summarised in the implicit definition
\begin{equation}\label{eq:definition:MRPI:set:state:dependent}
	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
\end{equation}
Thus an disturbance invariant set is a type of robust positive invariant (RPI) set. In many applications we are interested in the largest such
set, denoted $\mathcal X^\infty$, which is given by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust positive invariant (MRPI) set and has been used extensively, for example to define terminal regions in 
robust model predictive control. Although analytical properties
of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets were introduced much later~\cite{DeSantis:1994,Kolmanovsky:1995,Blanchini:1994}. 
%\note{You commented 'check', I didn't know what that meant.}
Earlier algorithms
did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, or 
did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
However for the case of disturbances that belong to a fixed set $\mathscr V$, methods of computing $\mathcal X^\infty$ are well established~\cite{blanchini:2007}.

This paper considers
sets of disturbances that depend on parameters. First we consider disturbance sets that are state dependent, of the form
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
\end{equation}
where $H(x)$ is a piecewise affine function. For the case that $\mathscr V=\mathcal V(x)$ we
provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss computation of $\mathcal X^\infty$.
The case of disturbances depending on states (or control inputs) is considered in~\cite{Kuntsevich:1995,rakovic06}, but the convexity analysis of this paper is novel. State dependent disturbance constraints can 
account for linearisation errors, as shown in section~\ref{sec:first:example}, as well as more general multiplicative parametric model uncertainty.

@@

The paper is structured as follows: In section~\ref{sec:parametrically:convex:set:operations} we
introduce the notion of \emph{parametric convexity} and discuss its implications, in particular as a condition 
for the convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
constraints is presented in section~\ref{sec:state:dep:MRPI}, and we also prove its finite determinability.
In section~\ref{sec:first:example} the algorithm is illustrated using an exemplar system, a magnetically levitated ball. The case of scaled disturbance constraints is discussed in section~\ref{sec:MRPI:parametrised}
where the algorithm for the parametrised MRPI set as well as the proof for its finite determinability
are also presented. Section~\ref{sec:second:example} illustrates the use of parametrised MRPI sets using
again the levitating ball example and illustrating a robustness analyses of the parametrised
MRPI sets with a numerical example. The paper is concluded in section~\ref{sec:conclusions}.

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
%By ${\bf{1}}$ we denote 
Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator. 

@@

In this section we discuss sets that depend on a state-like parameter (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extend the existing set algebra~\cite{blanchini:2007} to 

@@

      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$ 

@@

    In the following we will need to be able to compute differences of sets
    analogous to the Pontryagin difference in~\cite{Kolmanovsky:1998} but using parametrised 
    sets, this is defined as follows:

@@

    Notice that for constant maps $T$
    definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
    well known Pontryagin difference.
    For parametric Pontryagin differences of convex sets and parametrically convex maps we have the following result.

@@

@@

@@

  Consider a point-to-set map defined by~\eqref{eq:PWA:distrubance:set}
    where, for now, $H$ is elementwise convex in $x\in \mathscr X\subseteq\mathbb R^n$, so that 
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for 
    $\lambda\in[0,1]$ and $x_1, x_2\in X$.  For such sets we have the following result:

@@

      The point-to-set map $\mathcal V (x)$ defined in~\eqref{eq:PWA:distrubance:set} is parametrically 
      convex for all $x\in X.$

@@

@@

      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ we note that

@@

\def\genmat{\Xi} \def\genvec{\xi}Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
Furthermore, we will see that if $\mathcal X$ is polyhedral and $\mathcal 
V(x)$ is point wise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
again a polytopic set. This will become more clear in the next section when we describe 
the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.

@@

\section{Maximal Robust Positive Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}

@@

$v\in\mathcal V(x)$ where $\mathcal V(x)$ is defined as in~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
Notice that the set $\mathcal V(x)$ is pointwise polytopic for finite $x\in\mathcal X_0$ and can hence be represented as the 

@@

has a piece-wise affine dependence on $x$ the vertices $v_i(x)$ are also piece-wise affine in $x$.

@@

requires to satisfy $\Psi x + v\in\mathcal X^\infty$ for all

@@

$\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}$ and 
\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}. 
I.e. we iteratively introduce 
constraints that separate all points for which the successor state can lie outside 
$\mathcal X_0$. So for the first iteration we need to enforce the constraint:

@@

\begin{equation}\begin{split}

@@

	&\genmat_{0,i}\Psi x + \underbrace{\max_{j} \genmat_{0,i} v_j(x)}_{v_{0,i}^\ast(x)} \leq \genvec_{0,i}.

@@

to each inequality.
Notice that $v_{0,i}^\ast(x)$ is not necessarily given by one unique maximiser, 

@@

Since each vertex is a piece-wise affine function of $x$ the maximum $v_{0,i}^\ast(x)$ will also

@@

\begin{multline}

@@

	i\in\mathcal I_0\}.
\end{multline}

@@

And we analogously define

@@

@@

@@

where we have 

@@

\begin{multline}
	v_{l,i}^\ast(x)=\max_j \genmat_{0,i}\Psi^{l-1}v_j(x)\\
	 = \begin{array}{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array}
	 = \begin{array}{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
\end{multline}

@@

In a closed form the iterates can be expressed as

@@

	=& \bigcap_{l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).

@@

$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and the set therefore is robustly positive invariant.

@@

Let the system constraints be contained in a band $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 

@@

with a piecewise affine $H$, 
then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$. Hence the MRPI set $\mathcal X^\infty 

@@

Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early
iterations the parametric Pontryagin difference can yield the empty set. The empty set however is
an admissible polytope, i.e. an admissible MRPI set. For the remainder of this proof we assume
that the MRPI set is non-empty. For this notice that on any compact set $\mathcal S\subset\mathbb R^n$ we
have $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact.

The proof has two main steps: First we will prove that $\mathcal X_p$ is compact for $p\leq n$
where $n$ is the state dimension. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
a $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_p$ and using $N = \tilde N$. For the first step, notice that the observability of
$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.

@@

\Omega = \left(\begin{array}{c}
\Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
\end{array}\right)

@@

having a trivial kernel. But this then implies that the set $\mathcal P_{n+1} = \{x: 
\Omega x\leq{\bf{1}}\wedge-\Omega x\leq{\bf{1}}\} = \bigcap_{l\leq n+1} \Psi^{-l} B$ is bounded.
Notice that the containment $\mathcal X_k\subseteq \mathcal P_k$ holds for all $k$ and hence
the set $\mathcal X_{n+1}$ is also bounded. The case that $\tilde N<n$ occurs when $\Gamma$
has more than rank one. To see that $D_k$ grows exponentially we use that $\mathcal V(\mathcal X_{n+1})$
is bounded, let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n+1})$ and let
$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_1$

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{(i)} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{(ii)}.

@@

Since $\Psi$ is asymptotically stable we know that $\bar\lambda<1$ and so we have 
$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = (i)$
which implies exponential growth of $D_k$ as long as $(ii)$ is bounded. Recall that we assume
that the MRPI set is non-empty.
Hence, to bound $(ii)$ we use $k\geq n+1$ where $(ii)\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
\frac{1}{1-\bar\lambda} K_2$ holds. This concludes the proof: We proved that $D_k$ grows exponentially,
that it contains an exponentially growing ball. We proved that the subtrahend is bounded inside a ball of
finite radius, and hence we conclude that after a finite number of iterations $N$ intersecting with $D_{N+1}$
will no longer change $\mathcal X_N$.

@@

We have seen that we can compute a the maximal robust positive invariant set $\mathcal X^\infty$ for linear 

@@

\caption{The maximal robust positive invariant set for the levitating ball system.}

@@

\section{Maximal Robust Positive Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}

>>>>

\section{Introduction}
The analytic properties of disturbance invariant sets have been widely
studied (e.g.~\cite{blanchini:2007}) 
since their introduction in~\cite{Glover:1971,bertsekas71}. A disturbance invariant set $\mathscr X$ is a subset of the 
state constraint set $\mathcal X_0\subseteq\mathbb R^n$ containing states $x$ of the perturbed linear system
\begin{equation}\label{eq:system:equation}
	x^+ = \Psi x + v
\end{equation}
(where $\Psi$ is Hurwitz, $x,x^+\in\mathcal X_0$, and 
$v\in\mathscr V$) such that the successor state $x^+$ is contained in the 
disturbance invariant set for all possible realisations of the 
unknown disturbance $v$. This is summarised in the implicit definition
\begin{equation}\label{eq:definition:MRPI:set:state:dependent}
	\mathscr X = \{x:\Psi x + v\in\mathscr X\; \forall v\in\mathscr V\}.
\end{equation}
Thus a disturbance invariant set is a type of robust positively invariant (RPI) set. 
In many applications we are interested in the largest such set, denoted $\mathcal X^\infty$, which is given 
by the union of all RPI sets $\mathscr X\subseteq\mathcal X^\infty$. This set is known as the maximal robust 
positively invariant (MRPI) set and has been used extensively, for example, to define terminal regions in 
robust model predictive control~\cite{mayne:2000}. Although analytical properties
of these sets were derived soon after their introduction, algorithms for numerically computing MRPI sets 
were introduced much later~\cite{Blanchini:1994,DeSantis:1994,Kolmanovsky:1998}. 
%\note{You commented 'check', I didn't know what that meant.}
Earlier algorithms did not guarantee finite determinability of $\mathcal X^\infty$, see e.g.~\cite{Blanchini:1990}, 
or did not guarantee to produce the maximal RPI set, e.g.~\cite{Blanchini:1991}. 
%
However for the case of disturbances belonging to a fixed set $\mathscr V$, methods of computing 
$\mathcal X^\infty$ are well established~\cite{blanchini:2007}.

This paper considers sets of disturbances that depend on
parameters. First we consider state-dependent sets,
\begin{equation}\label{eq:PWA:distrubance:set}
	\mathcal V(x) = \left\{v: Gv\leq H(x)\right\},
\end{equation}
where $G$ is a real matrix,
%$G\in\mathbb R^{n_G\times n_v}$, 
$H(x)$ is a piecewise affine function, and the inequality applies elementwise. For the case that $\mathscr V=\mathcal V(x)$ we
provide conditions for convexity and finite determination of $\mathcal X^\infty$ and discuss 
computation of $\mathcal X^\infty$. The case of disturbances depending on states (or control inputs) 
is considered in~\cite{Kuntsevich:1995,rakovic06} but the convexity
analysis of this paper and the associated computational approach are novel. 
State dependent disturbance constraints can account for linearisation errors, as shown in section~\ref{sec:first:example}, 
as well as more general multiplicative parametric model uncertainty.

@@

The structure of the paper is as follows: We introduce the notion of \emph{parametric convexity} In
Section~\ref{sec:parametrically:convex:set:operations} and discuss its implications, in particular as a condition 
for convexity of the MRPI set. The algorithm to compute the MRPI set for state dependent disturbance
constraints and its finite determinability are discussed in Section~\ref{sec:state:dep:MRPI}.
Section~\ref{sec:first:example} illustrates the algorithm using the example of a magnetically 
levitated ball. The case of scaled disturbance constraints is discussed in Section~\ref{sec:MRPI:parametrised},
which gives the algorithm for computing the parametrised MRPI set and
proves its finite determinability. Section~\ref{sec:second:example} illustrates the use of
parametrised MRPI sets using the levitating ball example, and illustrates a robustness analysis of the parametrised
MRPI sets with a numerical example. Section~\ref{sec:conclusions}
provides conclusions.

Throughout this paper we refer to sets that can be represented as intersections of finite numbers of half spaces as polyhedra, and to bounded polyhedra as polytopic sets.
Also ${\bf{1}}$ denotes the column vector of ones in appropriate dimensions, and $\wedge$ is the logical AND operator.

@@

This section discusses sets that depend on a state-like parameter (so called point-to-set maps, 
see~\cite{Hogan:1973}), and extends the existing set algebra~\cite{blanchini:2007} to 

@@

      Let $X\subseteq\mathbb R^n, Y\subseteq\mathbb R^m$, let $\mathcal P(Y)$ denote the power set of $Y$, 

@@

The difference of sets can be defined for parametrised sets analogously to the Pontryagin difference~\cite{Kolmanovsky:1998} as follows:

@@

    Notice that, for a constant map $T$, the definition~\eqref{eq:definition:parametric:pontryagin:difference} is equivalent to the 
    well-known Pontryagin difference.
    For the parametric Pontryagin difference of a convex set and a parametrically convex map we have the following result.

@@

\[%      \begin{equation}

@@

\]%      \end{equation}

@@

  % Consider a point-to-set map~\eqref{eq:PWA:distrubance:set},
  %   where $H$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$, with elements $H_i(x)$ satisfying
  %   $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$, for all    $\lambda\in[0,1]$, and $x_1, x_2\in\mathcal X$.  For such sets we have the result:
%A family of parametrically convex sets is defined as follows.

@@

      The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} is parametrically 
      convex for all $x\in \mathcal X$ if $H(x)$ is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~if each element $H_i(x)$ of $H(x)$ satisfies
    $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$).

@@

    % \begin{thm}\label{thm:convex:parametric:set}
    %   The point-to-set map $\mathcal V (x)$ defined by~\eqref{eq:PWA:distrubance:set} for a function $H(x)$ that is elementwise convex in $x\in \mathcal X\subset \mathbb R^n$ (i.e.~each element $H_i(x)$ of $H(x)$ satisfies
    % $H_i(\lambda x_1+(1-\lambda)x_2)\leq \lambda H_i(x_1)+(1-\lambda)H_i(x_2)$ for all    $\lambda\in[0,1]$ and $x_1, x_2\in\mathcal X$) is parametrically 
    %   convex for all $x\in \mathcal X$.
    % \end{thm}

@@

      \lambda\mathcal V(x_1) \oplus(1-\lambda)\mathcal V(x_2)$ for all $\lambda \in [0,1]$ and $x_1, x_2\in\mathcal X$ we note that

@@

\def\genmat{\Xi} \def\genvec{\xi}
% Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
% and~\ref{thm:convex:parametric:set} imply that the parametric Pontryagin difference between a convex set $\mathcal X$ and 
% the point-to-set map $\mathcal V(x)$, i.e. $\mathcal X\ominus \mathcal V(\mathcal X)$, is a convex set.
% Furthermore, we will see that if $\mathcal X$ is polytopic and $\mathcal 
% V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
% again a polytopic set. This will become more clear in the next section when we describe 
% the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.
Lemmas~\ref{thm:convexity:of:pontryagin:difference} 
and~\ref{thm:convex:parametric:set} imply that, if $\mathcal V(x)$ is defined by \eqref{eq:PWA:distrubance:set} in terms of an elementwise convex function $H(x)$, then the parametric Pontryagin difference $\mathcal X\ominus \mathcal V(\mathcal X)$
is a convex set.
Furthermore, we will see in the next section that, if $\mathcal X$ is polytopic and $\mathcal 
V(x)$ is pointwise polytopic, then $\mathcal X\ominus\mathcal V(\mathcal X)$ is 
again a polytopic set. 
%This will become more clear in the next section when we describe 
%the computation of the MRPI set~\eqref{eq:definition:MRPI:set:state:dependent}.

@@

\section{Maximal Robust Positively Invariant Sets for State Dependent Disturbance}\label{sec:state:dep:MRPI}

@@

$v\in\mathcal V(x)$ where $\mathcal V(x)$ is a parametrically convex point-to-set map defined by~\eqref{eq:PWA:distrubance:set} with a piecewise affine $H(x)$.
Notice that the set $\mathcal V(x)$ is pointwise polytopic 
%\note{is it necessary to assume that $\mathcal V(x)$ is bounded $\forall x\in\mathcal X_0$?}
for finite $x\in\mathcal X_0$ and can hence be represented as the 

@@

has a piecewise affine dependence on $x$ the vertices $v_i(x)$ are also piecewise affine in $x$.

@@

is required to satisfy $\Psi x + v\in\mathcal X^\infty$ for all

@@

\mathcal X_0 = \{x:\;\genmat_{0,i}x\leq \genvec_{0,i}\,\forall i\in\mathcal I_0\}
and
recursively \emph{cut off} points that cannot satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
%\emph{cut off} all points that do not satisfy the invariance condition in $k$ steps, $k\in\mathbb N$. 
%So that all points remaining satisfy the invariance condition~\eqref{eq:definition:MRPI:set:state:dependent}
by iteratively introducing
constraints that exclude all points for which the successor state can lie outside 
$\mathcal X_0$. The first iteration enforces the constraint:

@@

\[%\begin{equation}

@@

	&\genmat_{0,i}\Psi x + \underbrace{\max_{j} \genmat_{0,i} v_j(x)}_{=v_{0,i}^\ast(x)} \leq \genvec_{0,i}.
\]%\end{equation}

@@

for each $i\in \mathcal I_0$.
Notice that $v_{0,i}^\ast(x)$ is not necessarily given by a unique maximiser, 

@@

Since each vertex is a piece-wise affine function of $x$, the maximum $v_{0,i}^\ast(x)$ will also

@@

\begin{multline*}

@@

	i\in\mathcal I_0\},
\end{multline*}

@@

and after $(k+1)$ iterations we have

@@

\[%\begin{equation}

@@

\]%\end{equation}

@@

where 

@@

%\begin{equation}
	v_{l,i}^\ast(x)&=\max_j \ \genmat_{0,i}\Psi^{l-1}v_j(x)
	 = \begin{array}[t]{rl} \max& \genmat_{0,i}\Psi^{l-1}v \\ \text{s.t.}& v\in\mathcal V(x)\end{array} \\
	 &= \begin{array}[t]{rl} \max& \genmat_{0,i}\tilde v\\ \text{s.t.}& \tilde v\in \Psi^{l-1}\mathcal V(x) \end{array}
%\end{equation}

@@

In closed form the iterates can be expressed as

@@

	=& \bigcap_{0\leq l\leq k+1}\left( \Psi^{-l} \mathcal X_0 \underset{i\leq l-1}{\bigominus} \Psi^i \mathcal V(\mathcal X_{l-1})\right).

@@

$\Psi x + v \in\mathcal X_N$ for all $v\in\mathcal V(x)$ and therefore $\mathcal X_N$ is robustly positively invariant.

@@

Let the state constraint set $\mathcal X_0$ be contained in a band: $\mathcal X_0\subseteq B=\{x:\Gamma x\leq{\bf{1}}\wedge 

@@

with a piecewise affine $H(x)$, 
then $\mathcal X_N\subseteq \mathcal X_{N+1}$ for a finite $N$, and hence the MRPI set $\mathcal X^\infty 

@@

From~\eqref{eq:set:iteration:state:dependent:constraints} it is clear that $\mathcal X^\infty = \emptyset$ if $\mathcal X_k =\emptyset$ for any $k\geq 0$.
%Notice that with~\eqref{eq:set:iteration:state:dependent:constraints} it is easy to see that in early iterations the parametric Pontryagin difference can yield the empty set. The empty set however is an admissible polytope, i.e. an admissible MRPI set. 
For the remainder of the proof we assume
that the MRPI set $\mathcal X^\infty$ is non-empty. For this we require that $\bigcup_{s\in\mathcal S}\mathcal V(s)$ is compact on any compact set $\mathcal S\subset\mathbb R^n$.

The proof has two main steps: First we prove that $\mathcal X_p$ is compact for $p\leq n$
where $n$ is the dimension of the state $x$. The second step is to prove that in~\eqref{eq:set:iteration:state:dependent:constraints}
the set $D_k$ grows exponentially, i.e. that for any given compact set $\mathcal C$ there exists
finite $\tilde N$ such that $\mathcal C\subseteq D_{\tilde N}$. The proof is concluded by setting 
$\mathcal C = \mathcal X_{\tilde N}$ and deducing that $N = \tilde N$.

For the first step, notice that observability of
$(\Psi,\Gamma)$ is equivalent to the observability matrix $\Omega$ having full rank, i.e.\ $\mathrm{rank}(\Omega) = \mathrm{rank}(\begin{bmatrix} \Gamma^T \ \cdots \ (\Gamma\Psi^{n-1})^T\end{bmatrix}) = n$.
% \[
% \Omega = \left(\begin{array}{c}
% \Gamma\\ \vdots \\ \Gamma\Psi^{n-1}
% \end{array}\right)
% \]
%having a trivial kernel. 
But  this implies that the set 

@@

\mathcal P_{n} = \{x: 
\Omega x\leq{\bf{1}}\wedge-\Omega x\leq{\bf{1}}\} = \bigcap_{0\leq l\leq n-1} \Psi^{-l} B

@@

is bounded, and since $\mathcal X_k\subseteq \mathcal P_k$ for all $k$, 
the set $\mathcal X_{n}$ is also bounded. The case that $\tilde N<n$ can occur if $\mathrm{rank}(\Gamma) > 1$.
%has more than rank one. 
More generally, to show that $D_k$ grows exponentially we use the boundedness of $\mathcal V(\mathcal X_{n})$. Let $K_1$ denote the smallest ball that contains $\mathcal V(\mathcal X_{n})$ and let
$\bar\lambda$ denote the magnitude of the largest eigenvalue of $\Psi$. Furthermore, let $K_2$

@@

D_k = \underbrace{\Psi^{-k}\mathcal X_0}_{=\mathcal S_1} \ominus \underbrace{\left(\bigoplus_{i\leq k-1} 
\Psi^i\mathcal V(\mathcal X_k)\right)}_{=\mathcal S_2}.

@@

Since $\Psi$ is asymptotically stable we have $\bar\lambda<1$ and therefore
$\bar\lambda^{-l}K_1\subseteq\Psi^{-l} K_1 \subseteq \Psi^{-l}\mathcal X_0 = \mathcal S_1$,
implying exponential growth of $D_k$ provided $\mathcal S_2$ is bounded. 
%Recall that we assume
%However the MRPI set is non-empty by assumption, and t
To bound $\mathcal S_2$ we note that $\mathcal S_2\subseteq \oplus_{i\leq k-1} \bar\lambda^i K_2 \subseteq
\frac{1}{1-\bar\lambda} K_2$ holds for $k\geq n$. This concludes the proof since $D_k$ grows exponentially,
%as it contains an exponentially growing ball. We proved that 
whereas $\mathcal X_k$ is contained in a ball of
finite radius, and hence we conclude from \eqref{eq:set:iteration:state:dependent:constraints} that 
$\mathcal X_{k+1} = \mathcal X _k$ for all $k\geq N$ and therefore $\mathcal X _N = \mathcal X^\infty$ for finite $N$.
%after a finite number of iterations $N$ intersecting with $D_{N+1}$
%will no longer change $\mathcal X_N$.

@@

We have seen that we can compute a the maximal robust positively invariant set $\mathcal X^\infty$ for linear 

@@

\caption{The maximal robust positively invariant set for the levitating ball system.}

@@

\section{Maximal Robust Positively Invariant Sets for Parametrised Disturbance}\label{sec:MRPI:parametrised}
